### 2018-10-29 pilot_manuscript.Rmd
wrote a little more

Research into politics, language, and media has illuminated the complex relationships between all three. Any politically-oriented discussion of language use as an implication of moral or poltical position assumes that langauge and ideology are intrisincally linked. Deborah Cameron [-@Cameron2006] points out the expressive nature of ideological beliefs and how that expression is conveyed through langauge, thus implying a connection between ideology and language. She goes on to criticize the notion that language is either the "pre-existing raw material" used to shape ideologies or the "post-hoc vehicle" for their propogation. Rather, the structure of language itself is shaped by ideology and social processes even when it is used to explain or express ideologies [@Cameron2006].

The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S. For example, Druckman, Jacobs, and Ostermeier (-@Druckman2004) investigated issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others. In their research, the authors consider "issue" as that which attmepts to persuade constituents to vote for the candidates based on their strengths in matters of public policy. "Image" priming, on the other hand, describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality [@Druckman2004]. The researchers found numerous examples of issue and image priming during the 1972 re-election campaign of Richard Nixon. They linked the Nixon adminstration's awareness of the issues for which the president had public support to the issues he should emphasize (and prime) during the campaign. Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence [@Druckman2004].

@Druckman2004 also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (read: priming) issues related to energy, defense, and the economy. This implies news media may affect perception of politicians based on where the media places emphasis. Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress [@Clinton2014]. Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their districts. As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the reserachers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival [@Clinton2014]. The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election [@Clinton2014].

@@

>>>>

Research into politics, language, and media has illuminated the complex relationships between all three. Any politically-oriented discussion of word occurence as an implication of moral or poltical position assumes that langauge and ideology are intrisincally linked. Deborah Cameron [-@Cameron2006] points out the expressive nature of ideological beliefs and how that expression is conveyed through langauge, thus implying a connection between ideology and language. She goes on to criticize the notion that language is either the "pre-existing raw material" used to shape ideologies or the "post-hoc vehicle" for their propogation. Rather, the structure of language itself is shaped by ideology and social processes even when it is used to explain or express ideologies [@Cameron2006].

The use of language both to express and further an ideological goal has been documented in the techniques employed by candidates for political office in the U.S. For example, Druckman, Jacobs, and Ostermeier (-@Druckman2004) investigated issue and image priming on the part of candidates as implied by the disproportionate attention candidates paid to particular issues over others. In their research, the authors consider "issues" as communication that attmepts to persuade constituents to vote for the candidates based on their strengths in matters of public policy. "Image" priming, on the other hand, describes techniques deployed in order to sway votes based on favorable aspects of the candidate's behavior and personality [@Druckman2004]. The researchers found numerous examples of issue and image priming during the 1972 re-election campaign of Richard Nixon. They linked the Nixon adminstration's awareness of the issues for which the president had public support to the issues he should emphasize (and prime) during the campaign. Likewise the researchers found evidence that Nixon's team was aware of negative evaluations of his warmth and trustworthiness, and thus took steps to prime his purportedly positive qualities, including strength and competence [@Druckman2004].

@Druckman2004 also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (read: priming) issues related to energy, defense, and the economy. This implies news media may affect perception of politicians based on where the media places emphasis. Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress [@Clinton2014]. Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their respective districts. As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the reserachers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival [@Clinton2014]. The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election [@Clinton2014].

@@

The Kavanaugh nomination, confirmation hearing, and eventual swearing-in, as well as the news media's coverage of all three events, feature many moral dimensions that likely differ depending on one's morals. On one side of the debate, Kavanaugh's Supreme Court tenure presents a prime oppurtunity to bring morality back into interpretation of the Constitution. Kavanaugh's confirmation creates a conservative stronghold among the justices on the court. Commentators have noted this might help advance a judicial agenda that backpedals certain rights previously upheld by the Supreme Court, including abortion and gay marriage - social issues challenged by their opponents at least partially on moral grounds. On the other side of the debate, the assault allegations have energized Kavanaugh's opponents to advocate for his rejection from the court owing to misdeeds resulting from Kavanaugh's own alleged lack of morals. Additionally, the moral duty of the Senate as the upper chamber in the U.S. legislature has been scrutinized in public discourse with respect to its handling of the assualt allegations vis-a-vis Kavanaugh's confirmation.
